\begin{flushleft}
    \section{Technical Solution}
        This section includes all the code relating to my Technical Solution, along with the two Json Formatted files which
        are used within my project. 

        \begin{itemize}
            \item \hyperref[sec:main.py]{main.py - pg. \pageref{sec:main.py}}
            \item \hyperref[sec:simulation.py]{simulation.py - pg. \pageref{sec:simulation.py}}
            \item \hyperref[sec:newAgent.py]{newAgent.py - pg. \pageref{sec:newAgent.py}}
            \item \hyperref[sec:enemy.py]{enemy.py - pg. \pageref{sec:enemy.py}}
            \item \hyperref[sec:worldClass.py]{worldClass.py - pg. \pageref{sec:worldClass.py}}
            \item \hyperref[sec:perlinNoise.py]{perlinNoise.py - pg. \pageref{sec:perlinNoise.py}}
            \item \hyperref[sec:deepqlearning.py]{deepqlearning.py - pg. \pageref{sec:deepqlearning.py}}
            \item \hyperref[sec:matrix.py]{matrix.py - pg. \pageref{sec:matrix.py}}
            \item \hyperref[sec:activations.py]{activations.py - pg. \pageref{sec:activations.py}}
            \item \hyperref[sec:datalogger.py]{datalogger.py - pg. \pageref{sec:datalogger.py}}
            \item \hyperref[sec:heap.py]{heap.py - pg. \pageref{sec:heap.py}}
            \item \hyperref[sec:plotData.py]{plotData.py - pg. \pageref{sec:plotData.py}}
            \item \hyperref[sec:paramfile]{Parameters File - pg. \pageref{sec:paramfile}}
            \item \hyperref[sec:rangefile]{Range File - pg. \pageref{sec:rangefile}}
        \end{itemize}

        Key Algorithms and Data Structures within my Program can be Located as shown below.

        \begin{itemize}
            \item Matrix Implementation - Contained within matrix.py - pg. \pageref{sec:matrix.py}
            \item Deque Implementation - deepqlearning.py - pg.\pageref{sec:deepqlearning.py} - Line. 255
            \item Heap Implementation - Contained within heap.py - pg. \pageref{sec:heap.py}
            \item Heap Sort - datalogger.py - pg. \pageref{sec:datalogger.py} - Line. 68
            \item Experience Replay - deepqlearning.py - pg. \pageref{sec:deepqlearning.py} - Line. 129
            \item Forward Propagation - deepqlearning.py - pg. \pageref{sec:deepqlearning.py} - Line. 226
            \item Backwards Propagation - deepqlearning.py - pg. \pageref{sec:deepqlearning.py} - Line. 231
            \item Abstract Base Class Activation - Contained within activations.py - pg. \pageref{sec:activations.py}
            \item Perlin Noise Algorithm - Contained within perlinNoise.py - pg. \pageref{sec:perlinNoise.py}
            \item Poisson Disc Sampling - worldClass.py - pg. \pageref{sec:worldClass.py} - Line. 116
            \item Threaded Terrain Generation - worldClass.py - pg. \pageref{sec:worldClass.py} - Line. 55
            \item Checking Parameters - simulation.py - pg. \pageref{sec:simulation.py} - Line. 145
            \item Matching Data Point Structure - datalogger.py - pg. \pageref{sec:datalogger.py} - Line. 25
        \end{itemize}

        The Full Source Code is available publically through the Link Below. \\
        \vspace{0.5cm}
        \centerline{\textit{https://github.com/TheTacBanana/CompSciNEA}}

        \label{sec:main.py}
        \subsection{main.py}
        \inputminted[frame=leftline,framesep=2mm,baselinestretch=1.2,fontsize=\normalsize,linenos,breaklines]{python}{../Scripts/main.py}

        \label{sec:simulation.py}
        \subsection{simulation.py}
        \inputminted[frame=leftline,framesep=2mm,baselinestretch=1.2,fontsize=\normalsize,linenos,breaklines]{python}{../Scripts/simulation.py}

        \label{sec:newAgent.py}
        \subsection{newAgent.py}
        \inputminted[frame=leftline,framesep=2mm,baselinestretch=1.2,fontsize=\normalsize,linenos,breaklines]{python}{../Scripts/newAgent.py}

        \label{sec:enemy.py}
        \subsection{enemy.py}
        \inputminted[frame=leftline,framesep=2mm,baselinestretch=1.2,fontsize=\normalsize,linenos,breaklines]{python}{../Scripts/enemy.py}

        \label{sec:worldClass.py}
        \subsection{worldClass.py}
        \inputminted[frame=leftline,framesep=2mm,baselinestretch=1.2,fontsize=\normalsize,linenos,breaklines]{python}{../Scripts/worldClass.py}

        \label{sec:perlinNoise.py}
        \subsection{perlinNoise.py}
        \inputminted[frame=leftline,framesep=2mm,baselinestretch=1.2,fontsize=\normalsize,linenos,breaklines]{python}{../Scripts/perlinNoise.py}

        \label{sec:deepqlearning.py}
        \subsection{deepqlearning.py}
        \inputminted[frame=leftline,framesep=2mm,baselinestretch=1.2,fontsize=\normalsize,linenos,breaklines]{python}{../Scripts/deepqlearning.py}

        \label{sec:matrix.py}
        \subsection{matrix.py}
        \inputminted[frame=leftline,framesep=2mm,baselinestretch=1.2,fontsize=\normalsize,linenos,breaklines]{python}{../Scripts/matrix.py}

        \label{sec:activations.py}
        \subsection{activations.py}
        \inputminted[frame=leftline,framesep=2mm,baselinestretch=1.2,fontsize=\normalsize,linenos,breaklines]{python}{../Scripts/activations.py}

        \label{sec:datalogger.py}
        \subsection{datalogger.py}
        \inputminted[frame=leftline,framesep=2mm,baselinestretch=1.2,fontsize=\normalsize,linenos,breaklines]{python}{../Scripts/datalogger.py}

        \label{sec:heap.py}
        \subsection{heap.py}
        \inputminted[frame=leftline,framesep=2mm,baselinestretch=1.2,fontsize=\normalsize,linenos,breaklines]{python}{../Scripts/heap.py}

        \label{sec:plotData.py}
        \subsection{plotData.py}
        \inputminted[frame=leftline,framesep=2mm,baselinestretch=1.2,fontsize=\normalsize,linenos,breaklines]{python}{../Scripts/plotData.py}

        \label{sec:paramfile}
        \subsection{Parameters File}
        \inputminted[frame=leftline,framesep=2mm,baselinestretch=1.2,fontsize=\normalsize,linenos]{json}{../Parameters/Default.param}

        \label{sec:rangefile}
        \subsection{Ranges File}
        \inputminted[frame=leftline,framesep=2mm,baselinestretch=1.2,fontsize=\normalsize,linenos]{json}{../Parameters/Range.param}

\end{flushleft}